\documentclass{article}

\newcommand{\D}{{\cal D}}
\newcommand{\N}{{\bf N}}
\renewcommand{\P}{{\bf P}}
\newcommand{\zo}{\{0,1\}}
\marginparwidth 0pt
\oddsidemargin  0pt
\evensidemargin  0pt
\marginparsep 0pt

\topmargin   0pt

\textwidth   6.5in
\textheight  8.5 in

%\usepackage[T1]{fontenc}
%\usepackage{times}
\usepackage{amsmath,amssymb,amsfonts,enumerate,amsthm}
\setlength{\textheight}{9in}
%\advance\textwidth by 2cm
%\advance\oddsidemargin by -1cm
%\advance\evensidemargin by -1cm
%\setlength{\parskip}{\medskipamount}
%\setlength{\parindent}{0pt}
\hyphenation{crypto-gra-phy} % can someone look it up in a dictionary?
% parameters: four corners, title, scribes' names
\newcommand{\handout}[7]{{
\begin{center}
\begin{minipage}{14cm}
    \setlength{\parindent}{0cm}%
    \fbox{\vbox{%
        {#1}%
        \hfill
        #2

        \center{\Large\bf{#5}}

        \emph{#3}\hfill #4
    }}%
    \vskip0pt
    \vbox{\hfill  #6}%
\end{minipage}
\end{center}
\vspace{2cm}
}}
\begin{document}

\handout{0368.4162: Introduction to Cryptography}
        %{Instructor: Ran Canetti}
        {}
        {\today}
        {}
        {Guidelines for Solutions of Problem Sets} % title

~Problem sets are an important part of the course, and are probably the best way
to understand the material. Please take them seriously. Here are some
guidelines for solutions:
\begin{enumerate}
\item
Please typeset your solutions. You can do it in either English or Hebrew;
English is recommended since it gives some practice in technical writing.
Still, please submit a hard copy of the solutions.
\item
You can think together about problems, but when it comes to writing,
please write the solutions on your own. If you thought up a solution together
with others, please indicate so in your solution, specifying who you worked
with.
\item
It is OK to use the literature for finding solution. If you used some reference literature, please indicate which.
\item
Try hard not to be late in handing in your solutions.
If you see you are going to be late, please notify us in advance.
\item
Some of the problems are simple recitations of the material learned in class.
Others require some thought, and some are even open-ended (namely, I am not
sure what the solution is). If you cannot solve a problem, please describe your solution attempts and where you got stuck.
\item
Finally, if you think you found a bug in a question, please write us  as
soon as possible. I'll post fixes on the website and announce them on the
mailing list.
%\item
%Unless specified otherwise, all questions have equal weight in the grade.
\end{enumerate}

\end{document}

